Stochastic blockmodels for relational events

### 2012-03-14 docs/slides/slides.tex
Add material to slides

\documentclass{beamer}
\usetheme{default}
\usepackage{tikz}
\usepackage{subfig}
\setlength{\unitlength}{\textwidth} 
\tikzstyle{vertex}=[auto=left,circle,fill=black!25,minimum size=20pt,inner sep=0pt]
\title[Blockmodels for relational events]%(optional, only for long titles)
{Stochastic blockmodels for relational events}
\subtitle{}
\author[DuBois, Christopher] % (optional, for multiple authors)
{Christopher~DuBois\inst{1} \and Carter~Butts\inst{2} \and Padhraic~Smyth\inst{3}}
\institute[] % (optional)
{
  \inst{1}%
Department of Statistics \\
University of California, Irvine
  \and
  \inst{2}%
Department of Sociology \\
University of California, Irvine
  \and
  \inst{2}%
Department of Computer Science \\
University of California, Irvine
}
\date[Sunbelt 2012] % (optional)
{Sunbelt 2012}
\subject{Informatik}
\begin{document}
\frame{\titlepage}

@@

\begin{itemize}
\item Above example: 2 dyadic events occurring among 4 nodes
\item Nodes may have covariates
\item Interested in inferences about the rate of particular events, conditioned on what we have observed
\end{itemize}
\end{frame}

\begin{frame}{Relational event models}

Multiplicative models for the hazard:
$$\log \lambda_{ij}(t | \cdot) = \boldsymbol{\beta}' \mathbf{s}(t,i,j)$$

Likelihood:

@@

\includegraphics[scale=.45]{../../figs/synthetic/unsorted}
\uncover<2->{\includegraphics[scale=.45]{../../figs/synthetic/mat}}
\uncover<3->{\includegraphics[scale=.45]{../../figs/synthetic/bm} }

\vspace{-.8cm}
\begin{align*}
\uncover<4->{
\mbox{Mixing rates} & & \boldsymbol{\eta} =& \left[
\begin {array}{cc}
 \eta_{11}& \eta_{12} \\
 \eta_{21}& \eta_{22} 
\end {array}
\right]
= \left[
\begin {array}{cc}
.8 & .2\\.2 & .8
\end {array}
\right] \\
}
\uncover<5->{
\mbox{Dyad (i,j)} &  & y_{ij} \sim& F(\eta_{z_i,z_j}) \\
}
\uncover<6->{
\mbox{Actor i's class} & & z_i \sim& \mbox{Categorical}(\pi)
}
\end{align*}

@@

>>>>

\documentclass{beamer}
\usetheme{default}
\usepackage{tikz}

\setlength{\unitlength}{\textwidth} 
\tikzstyle{vertex}=[auto=left,circle,fill=black!25,minimum size=20pt,inner sep=0pt]
\title{Stochastic blockmodels for relational events}
% \subtitle{}
\author[DuBois, Christopher] % (optional, for multiple authors)
{Christopher~DuBois\inst{1} \and Carter~Butts\inst{2} \and Padhraic~Smyth\inst{3}}
\institute[] % (optional)
{
  \inst{1}%
Department of Statistics \\
University of California, Irvine
  \and
  \inst{2}%
Department of Sociology \\
University of California, Irvine
  \and
  \inst{2}%
Department of Computer Science \\
University of California, Irvine
}
\date[Sunbelt 2012] % (optional)
{Sunbelt 2012}
\begin{document}
\frame{\titlepage}

@@

\begin{itemize}
\item Above example: 2 dyadic events occurring among 4 nodes
\item Nodes and edges may have covariates
\item Interested in inferences about the rate of particular events, conditioned on what we have observed
\end{itemize}
\end{frame}

\begin{frame}{Relational event models: Modeling the \emph{hazard}}
Multiplicative models for the hazard of a dyad $(i,j)$:
$$\log \lambda_{ij}(t | \cdot) = \boldsymbol{\beta}' \mathbf{s}(t,i,j)$$
\begin{itemize}
\item $\lambda_{ij}(t | \cdot)$: ``rate'' of interaction from $i$ to
  $j$ at time $t$
\item $\boldsymbol{\beta}$: vector of model parameters
\item $\mathbf{s}(t,i,j)$: vector of sufficient statistics for $(i,j)$
  given the events before time $t$
\end{itemize}
\end{frame}

\begin{frame}{Relational event models: Likelihood}

@@

\uncover<2->{\includegraphics[scale=.45]{../../figs/synthetic/unsorted}}
\uncover<3->{\includegraphics[scale=.45]{../../figs/synthetic/mat}}
\uncover<4->{\includegraphics[scale=.45]{../../figs/synthetic/bm} }

\vspace{-.8cm}
\begin{align*}
\uncover<5->{
\mbox{Mixing rates} & & \boldsymbol{\eta} =& \left[
\begin {array}{cc}
 \eta_{11}& \eta_{12} \\
 \eta_{21}& \eta_{22} 
\end {array}
\right]
= \left[
\begin {array}{cc}
.8 & .2\\.2 & .8
\end {array}
\right] \\
}
\uncover<6->{
\mbox{Dyad (i,j)} &  & y_{ij} \sim& F(\eta_{z_i,z_j}) \\
}
\uncover<7->{
\mbox{Actor i's class} & & z_i \sim& \mbox{Categorical}(\pi)
}
\end{align*}

@@

\begin{frame}{Model adequacy}
Plot parameter estimates for winning model
Compare to fitting a single relational event model
\end{frame}
